Supplemental Materials for: \\ Large scale risks from pesticides in small streams

### 2016-12-28 supplement/Supplemental_Materials.tex
final fixes before submission
revised technical notes

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs} % table rulers
\usepackage{longtable} % multipage tables
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{float} % for [H]
\usepackage{array, ragged2e}
\newcolumntype{R}[1]{>{\RaggedLeft\arraybackslash}p{#1}} % right aling column with fixed width

% Continuous figure counting (instead of per cahpter)
\usepackage{chngcntr}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}
% Add 'S' before figure/table numbering
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

%% -------------------------------------------------------------------------
\title{Supplemental Materials for the paper: \\ Pesticide exposure in small streams in Germany}
\author{Eduard Szöcs, Marvin Brinke, Bilgin Karaoglan, Ralf B. Schäfer}
\date{}

@@

>>>>

\documentclass[pdftex,
	a4paper,
	titlepage=false]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs} % table rulers
\usepackage{longtable} % multipage tables
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{float} % for [H]
\usepackage{array, ragged2e}
\newcolumntype{R}[1]{>{\RaggedLeft\arraybackslash}p{#1}} % right aling column with fixed width

% Continuous figure counting (instead of per cahpter)
\usepackage{chngcntr}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}
% Add 'S' before figure/table numbering
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thepage}{S\arabic{page}}

@@

% affiliations
\usepackage[affil-it]{authblk}

% counts
% http://ctan.mackichan.com/macros/latex/contrib/caption/totalcount.pdf
\usepackage[figure,table, page]{totalcount}

%% -------------------------------------------------------------------------
\title{Supplemental Materials for: \\ Large scale risks from pesticides in small streams}
\author{Eduard Szöcs%
  \thanks{Corresponding author, Email: \texttt{szoecs@uni-landau.de}}}
\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Germany}

\author{Marvin Brinke}
\affil{German Federal Institute of Hydrology (BfG), Koblenz, Germany}

\author{Bilgin Karaoglan}
\affil{German Environment Agency (UBA), Dessau-Roßlau, Germany}

\author[1]{Ralf B. Schäfer}

@@

\vfill
\begin{description}
	\item[Number of pages: ] \totalpages
	\item[Number of figures: ] \totalfigures
	\item[Number of tables: ] \totaltables
\end{description}
% increase page counter by 1
\setcounter{page}{2}
